---
title       : Course 9 project slides
subtitle    : 
author      : Alessandro Destefanis
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## To be done

Scope of the project is the creation of a simple R Shiny application and the presentation of the application thanks to slides.

Aim of the application is to perform an exploration analysis of the mtcars dataset.

```{r }
str(mtcars)
```

--- .class #id 

## Code used 1

Here's the code inside sidebarLayout() function in ui.R

```{r eval=FALSE}
sidebarPanel(
        selectInput('x', 'X', choices = columns, selected = "wt"),
        selectInput('y', 'Y', choices = columns, selected = "mpg"),
        selectInput('color', 'Color', choices = columns, selected = "cyl"),
        selectInput('facet_row', 'Facet Row', c(None = '.', columns), selected = "carb"),
        selectInput('facet_col', 'Facet Column', c(None = '.', columns)),
        helpText("In order to explore the dataset please select the variables you desire to be showed.")
    ),
    mainPanel(
       plotlyOutput("carsPlot")
```

--- .class #id 

## Code used 2

Here's the code used to define the graph to be printed, inside server.R

```{r eval=FALSE}
output$carsPlot <- renderPlotly({
    
      p <- ggplot(mtcars, aes_string(x = input$x, y = input$y, color = input$color)) + geom_point()
      facets <- paste(input$facet_row, '~', input$facet_col)
      if (facets != '. ~ .')
          p <- p + facet_grid(facets)
      
      ggplotly(p) %>% 
          layout(height = input$plotHeight, autosize=TRUE)
  })
```

--- .class #id 

## The imput panel

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(shiny)
library(plotly)

data("mtcars")
columns <- names(mtcars)

# Define UI for application that draws a histogram
shinyUI(fluidPage(
  
  sidebarLayout(
    sidebarPanel(
        selectInput('x', 'X', choices = columns, selected = "wt"),
        selectInput('y', 'Y', choices = columns, selected = "mpg"),
        selectInput('color', 'Color', choices = columns, selected = "cyl"),
        selectInput('facet_row', 'Facet Row', c(None = '.', columns), selected = "carb"),
        selectInput('facet_col', 'Facet Column', c(None = '.', columns)),
        helpText("In order to explore the dataset please select the variables you desire to be showed.")
    ),
    
    # Show a plot of the generated distribution
    mainPanel(
       plotlyOutput("carsPlot")
    )
  )
))
```
